Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-03-22 latex/comp_or.tex
Paper Comp OR updated

Let $p_i.H$ be the maximum height for each pallet to be built, which depends on the size of the aircraft and the pallet position along the cargo bay; each {\it 463l} pallet has a width $p_i.W = 2.15m$ and a length of $p_i.L = 2.65m$.

\begin{equation} \label{eq:3dof}
	\mbox{minimize}\ \Bigg [ p_i.W \times p_i.H \times p_i.L - \sum_{j \in p_i} t_j.w \times t_j.h \times t_j.l \ \Bigg ]
\end{equation}

@@

\begin{equation} \label{eq:3dl}
	s.t.: \sum_{j \in p_i} t_j.l \leq p_i.L 
\end{equation}

>>>>

Let $p_i.H$ be the maximum height for each pallet to be built, which depends on the size of the aircraft and the pallet position along the cargo bay; each {\it 463l} pallet has a width $p_i.W = 2.15m$ and a depth of $p_i.D = 2.65m$.

\begin{equation} \label{eq:3dof}
	\mbox{minimize}\ \Bigg [ p_i.W \times p_i.H \times p_i.D - \sum_{j \in p_i} t_j.w \times t_j.h \times t_j.d \ \Bigg ]
\end{equation}

@@

\begin{equation} \label{eq:3dl}
	s.t.: \sum_{j \in p_i} t_j.d \leq p_i.D 
\end{equation}
